Relationship between solar wind, $D_{st}$, and plasmasphere mass density on one-hour time scales

### 2015-09-03 paper.tex
Small fixes. Adding F10.7 figures to paper.

Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.  A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.  The linear correlation is found to be $0.87$ (? plot says 0.94!).  In comparison, \cite{Takahashi2010} found a correlation coefficient of $0.94$ using measurements from all satellites in the time interval of 1980 through 1991.

@@

In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.  The minimum $D_{st}$ median is $-48$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is ~2 amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.  Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.

@@

This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours. Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after. Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40nT$. The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average. The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average. Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack. A subset of longer duration events will be looked at later.

@@

Neither of these seem to indicate anything too significant, so looking at $D_{st}$ events instead to look for something that causes a significant change in Mass Density results in Figure \ref{Dspec}. This shows that by either looking only at $D_{st}$ events that last longer than an hour (left) or at events where the onset condition is $D_{st}<-80nT$, a spike in mass density is seen, but also a definite lack of data availability to the point where that spike may be coming from less than five of the total 143 events.

Unfortunately there are no events in this time frame that are longer than 12 hours with $D_{st}$ minima lower than $-80nT$ that have existing mass density data around onset, so an analysis of this particular relationship can't be made.

@@

\subsection{Change in $\rho_{eq}$}
If instead of looking for events based on a threshold of $\rho_{eq}$, we instead look for a certain amount of change in $\rho_{eq}$ as the basis for event onset, we get Figure \ref{rhochange}.

Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively. This shows a distinct lack of correlation in either case to a change in $D_{st}$. The percent change in $\rho_{eq}$ does, however, seem to be preconditioned by changes in $B_z$ and $F_{10.7}$.

@@

Taking this re-created data set and subtracting it from the original should remove the $F_{10.7}$ dependence from the data, and allow for a less biased analysis of the relationship between $D_{st}$ and $\rho_{eq}$. Figure \ref{nof107} shows the stack plot for the reduced $F_{10.7}$, where a more distinct peak after event onset can be seen. It also shows what that removed trend looks like, of the form $\rho_{eq}-\rho_{eq,F_{10.7}}$.

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-d80.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70~amu/cm^3$.}
\label{Dspec}
\end{figure}

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-dst-nof107.eps}
\includegraphics[scale=0.40]{paperfigures/f107removed.eps}
\caption{$D_{st}$ events where $\rho_{eq}$ has $F_{10.7}$ dependence removed, and Difference between original $\rho_{eq}$ and $F_{10.7}$-less $\rho_{eq}$}
\label{nof107}
\end{figure}

>>>>

Figure~\ref{ccplot:a} shows the long-term trends of $log(\rho_{eq})$ and $F_{10.7}$ computed using the median values in 27-day (non-overalpping?) windows using all non--fill hourly values.  A scatter plot of these two lines is shown in Figure~\ref{ccplot:b}.  The linear correlation is found to be $0.94$ matching the value found by \cite{Takahashi2010} who used measurements from all satellites in the time interval of 1980 through 1991.

@@

In the upper panel of \label{DailyAverages}, $D_{st}$ events are shown.  The minimum $D_{st}$ median is $-48$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$, although the magnitude of increase observed here is $\sim2$ amu/cm$^3$ instead of the value of ~10 amu/cm$^3$ found in \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute its median and error bars.  Note that for $D_{st}$, the number of measurements used in computing the medians is much larger as we use all available $D_{st}$ measurements instead of restricting to only values where a non--fill $\rho_{eq}$ value existed.

@@

This method finds 669 such periods between May 1983 and August 1991 with an average duration of 9 hours and a median duration of 3 hours. Figure \ref{Storms} shows the average values of all events over a window of 24 hours before onset and 48 hours after. Figure \ref{Storms}a shows events selected by looking for event onsets where $D_{st}$ crossed a threshold of $-40$~nT. The dashed red lines indicate plus and minus one standard deviation of values from all events that went into the average. The final plot in the stack shows both $\rho_{eq}$ and a bar plot of how many valid data points went into the $\rho_{eq}$ average. Since $\rho_{eq}$ comes from a sparser dataset, it has less valid points contributing to the averages than the other parameters in the stack. A subset of longer duration events will be looked at later.

@@

@@

\subsection{Change in $\rho_{eq}$}
Instead of looking for events based on a threshold of $\rho_{eq}$, we instead looked for a certain amount of change in $\rho_{eq}$ as the basis for event onset. Both raw change and percent change were done in case of bias towards high or low $\rho_{eq}$ periods, respectively, but neither showed any correlation to a change in $D_{st}$.

@@

Figure \ref{f107bin} takes the events and bins them by the value of $F_{10.7}$ at event onset, then looks at both $\rho_{eq}$ and $B_z$. A significant difference is seen in $\rho_{eq}$ between events taking place during periods of high $F_{10.7}$ and low $F_{10.7}$, while a much less significant, but still noticeable, difference is seen in $B_z$.

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/stormavs-d80.eps}
\rule[1ex]{5cm}{1pt}
\includegraphics[scale=0.40]{paperfigures/stormavs-m70.eps}
\caption{(a) Same as Figure \ref{Storms}(a) except with constraint that $D_{st}$ crossed below $-80$~nT (b) Same as Figure \ref{Storms}(b) except for constrain that $\rho_{eq}$ crossed above $70$~amu/cm$^3$.}
\label{Dspec}
\end{figure}

@@

\begin{figure}[tp!]
\centering
\includegraphics[scale=0.40]{paperfigures/HighLowF107rho.eps}
\includegraphics[scale=0.40]{paperfigures/HighLowF107Bz.eps}
\includegraphics[scale=0.40]{paperfigures/HighLowF107valid.eps}
\caption{Binning events by $F_{10.7}$ value at onset for $\rho_{eq}$ and, in the middle panel, $B_z$. Lower panel shows number of valid points in each bin}
\label{f107bin}
\end{figure}
